Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2020-09-21 paper/paper.Rmd
spelling

Differences in behavior among individuals (i.e. behavioral syndromes sensu [@sih2004behavioral]) can have remarkable consequences on ecological and evolutionary processes [@wolf_animal_2012]. For vertebrate dispersed plants, animal behavior will inﬂuence seed shadows and few species, or even individuals, might provide unique, high value dispersal services by moving farther distances from parental plants [@schupp_seed_2010]. Long distance dispersal (LDD) events are crucial to reaching suitable sites to germinate and establish and to colonize new habitats [@nathan2006long]. Furthermore, rare events (often overlooked) are critical for dispersal and might have a large effect on resulting plant demography [@loayza2014seed]. Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patters of seed dispersal.

>>>>

Differences in behavior among individuals (i.e. behavioral syndromes sensu [@sih2004behavioral]) can have remarkable consequences on ecological and evolutionary processes [@wolf_animal_2012]. For vertebrate dispersed plants, animal behavior will inﬂuence seed shadows and few species, or even individuals, might provide unique, high value dispersal services by moving farther distances from parental plants [@schupp_seed_2010]. Long distance dispersal (LDD) events are crucial to reaching suitable sites to germinate and establish and to colonize new habitats [@nathan2006long]. Furthermore, rare events (often overlooked) are critical for dispersal and might have a large effect on resulting plant demography [@loayza2014seed]. Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patterns of seed dispersal.
